### 2018-05-20 Paper/examples.tex
...

The borehole function is a benchmark reference problem in sensitivity analysis. It models the discharge
of water ($\mathcal{Q}$) through a borehole in terms of geometrical and physical parameters:

\be
\mathcal{Q} = \frac{2\pi T_u(H_u - H_l)}{\ln\left(\frac{r}{r_w}\right)\left(1 +
\frac{2LT_u}{\ln\left(\frac{r}{r_w}\right)r_w^2K_w} + \frac{T_u}{T_l}\right)}
\label{eq:bore}
\ee

\noindent The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
in the right hand side of~\eqref{eq:bore} are considered 
as uncertain. Thus, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
\[
   \vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T.
\] 
Table~\ref{tab:bore} provides distributions of the uncertain inputparameters.

>>>>

The borehole function is a benchmark reference problem in sensitivity analysis.
It models the discharge of water ($\mathcal{Q}$) through a borehole in terms of
geometrical and physical parameters:
\be
\mathcal{Q} = \frac{\displaystyle
2\pi T_u(H_u - H_l)}{\displaystyle
\ln({r}/{r_w})\Big[1 +
\frac{2LT_u}{
\ln({r}/{r_w})r_w^2K_w} + \frac{T_u}{T_l}\Big]}
\label{eq:bore}
\ee
The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
in the right hand side of~\eqref{eq:bore} are considered 
as uncertain. Thus, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
\[
   \vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T.
\] 
Table~\ref{tab:bore} provides distributions of the uncertain inputparameters.
